Need a good title.

### 2018-02-14 ms.tex
temp pushing before meeting

\begin{tabular}{|c|c|c|}
\hline
Type of RE	& Formula	& Platform	\\
\hline

Single site intercept	  &	1 $\mid$ sp	& gls, lme4 \\
Single site intercept and uncorrelated slopes		&  1 $\mid$ sp + X $\mid$ sp		& lme4 \\
Single site intercept and correlated slopes 			& 1 + X $\mid$ sp					& lme4 \\
\hline
Multiple site intercept 									&  1 $\mid$ sp 						& pez, lme4 \\
Multiple site intercept and uncorrelated slopes 	&  1 $\mid$ sp + X $\mid$ sp 		& pez, lme4 \\
Multiple site intercept and uncorrelated slopes 	& 	1 + X $\mid$ sp					& lme4 \\
ditto with site interaction								& ditto above $\mid$ sp:site		& ditto above \\
\hline
% \vspace{1in}
\end{tabular}

We generate test data using a simple glmm framework that varies in complexity in random effect described in Table 1 \ml{macro this}. All simulations and fits were performed with R.

\subsection{Model Fitting}
\ml{platform/model equivalence}

...

>>>>

% \begin{table}
% \begin{center}
\begin{tabular}{|c|c|c|}
\hline
Type of RE	& Formula	& Platform	\\
\hline

Single site intercept	  &	1 $\mid$ sp	& gls, lme4 \\
Single site intercept and uncorrelated slopes		&  1 $\mid$ sp + trait $\mid$ sp		& lme4 \\
Single site intercept and correlated slopes 			& 1 + trait $\mid$ sp					& lme4 \\
\hline
Multiple site intercept 									&  1 $\mid$ sp 						& pez, lme4 \\
Multiple site intercept and uncorrelated slopes 	&  1 $\mid$ sp + trait $\mid$ sp 		& pez, lme4 \\
Multiple site intercept and correlated slopes 	& 	1 + trait $\mid$ sp					& lme4 \\
\hline
\end{tabular}
% \vspace{1in}
% ditto with site interaction								& ditto above $\mid$ sp:site		& ditto above \\
% \end{center}
% \end{table}

The simulation models is based on glmm framework described in \ml{eq labels 3-5}.   
To construct the simulation model, let $n$ be the number of species distributed among $m$ sites.
Let $Y$ be the $mn \times 1$ vectors of response trait.  
We generate test data using three different $n$ (20, 100, 500) and two different $m$ (1, 20) using a simple glmm framework that varies in complexity in random effect described in \ml{Table 1, macro this with labels}. 
We also extend the multiple site models described in \ml{Table 1} with species by site interaction random effects. 
All simulations and fits were performed with R.

\subsection{Model Fitting}
